## `r fontawesome::fa("fas fa-house-user", fill = "steelblue")` About {- .tabset .tabset-pills}

### Overview {-}

The **`CRAN search`** project is to perform package search available in the Comprehensive R Archive Network (CRAN) repositorio for programming language R. The collected data is obtained by the **`tools::CRAN_package_db()`** and selected only a few columns to perform the search of the theme of interest.

In the following table, you can check a brief structure of the data frame collected from the packages available in CRAN as number of rows and the frequency of words greater than 3 characters for the *title*, *description*, and *license* columns. An in-depth investigation of the data is at the discretion of the reader.

``` {r}
knitr::kable(df_join)
```

### Author {-}

##### Author {-}

``` {r}
knitr::kable(
    data.frame(
        name = c("author", "website", "github"),
        contact = c(
            "Bruno Faria",
            "https://brunofariadf.github.io/",
            "https://github.com/brunofariadf/"
        ),
    check.names = FALSE))
```

##### Project {-}

- cran-search

##### Review {-}

- News

##### License {-}

- MIT