## `r fontawesome::fa("fas fa-house-user", fill = "steelblue")` About {- .tabset .tabset-pills}

### Overview {-}

The **`cran-search`** project aims to provide a database to perform a package search for the R programming language in the Comprehensive R Archive Network (CRAN) repository. The collected data are obtained by the tools::CRAN_package_db() function and selected only a few columns to perform the search for the topic of interest.

In the following table, it is possible to verify a brief structure of the data frame collected with packages available in CRAN. For example, the number of rows and columns, and the frequency of words longer than 3 or 4 characters for the column named *title*, *description*, and *license*. A depth investigation of the data is at the discretion of the reader.

``` {r}
knitr::kable(df_join)
```

### Author {-}

##### Author {-}

``` {r}
knitr::kable(
    data.frame(
        name = c("author", "website", "github"),
        url = c(
            "Bruno Faria",
            "https://brunofariadf.github.io/",
            "https://github.com/brunofariadf/"
        ),
    check.names = FALSE))
```

##### Project {-}

``` {r}
knitr::kable(
    data.frame(
        name = c("main", "review", "license"),
        url = c(
            "[cran-search](https://github.com/brunofariadf/cran-search)",
            "[News](https://github.com/brunofariadf/cran-search/blob/main/NEWS.md)",
            "[MIT](https://github.com/brunofariadf/cran-search/blob/main/LICENSE)"
        ),
    check.names = FALSE))
```

<!-- - [cran-search](https://github.com/brunofariadf/cran-search)

##### Review {-}

- [News](https://github.com/brunofariadf/cran-search/blob/main/NEWS.md)

##### License {-}

- [MIT](https://github.com/brunofariadf/cran-search/blob/main/LICENSE) -->
